Analysing Constraint Grammars with a SAT-solver

### 2016-02-12 paper/lrec/implementation.tex
right path for cg.bib
add stuff about lexical entries and clitics

>>>>

\paragraph{Choosing the readings}

Earlier we have shown an example with 5 readings (\texttt{det def}, \texttt{noun sg}, ...). In the real implementation, we operate between hundreds and thousands of readings. This is very much dependent on language: Dutch, the simplest language, has 336 readings.

We expand an Apertium morphological lexicon, throw away the word forms and take all the analyses. An exception is when the grammar contains rules that target a specific lemma or word form.
A simple solution is to retain the lemmas and word forms only for those entries where it is specified in the grammar, and otherwise leave them out. For example, the grammar may contain the following list:

\begin{itemize}
 \item[] \texttt{LIST ZijnVerb = ("zijn" vbser pres pl) ;}
\end{itemize}

Clearly there is something special about the verb \emph{zijn}, not just any verb. Looking at the lexicon, we find \emph{zijn} in the following entries:

\begin{itemize}
 \item[] \begin{verbatim}zijn:zijn<det><pos><mfn><pl>
zijn:zijn<det><pos><mfn><sg>
zijn:zijn<vbser><inf>
zijn:zijn<vbser><pres><pl>
\end{verbatim}
\end{itemize}

Thus we add special entries for these: in addition to the anonymous
 \texttt{<det><pos><mfn><pl>} reading, we add \texttt{<"zijn"><det><pos><mfn><pl>}.

 However, for languages with more readings, this may not be feasible. For instance, the Spanish lexicon has a high number of readings mostly because of the verbs: in addition to the verb forms, there are clitics attached to them. The number of verb readings without clitics is 213, and with clitics 1572.

 In our experience,  even ignoring the clitics doubles the amount of readings.

Another note: the readings in grammar can be underspecified (e.g. ``verb sg''), whereas the lexicon only gives us fully specified (``verb pres p2 sg'') readings.
